Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-14 02_Paper/paper.tex
Final revision. Added Author contribution
add well.
Correction 14.12.2020

\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-2630. {\it E-mail address:} fabian.steinberg@uni-siegen.de}

@@

\subsection{Decision Tree}
Decision Trees are essentially binary trees, which work with the input
features at the roots, decisions are made by moving
up the tree to top leaves. At every branch in the tree, a decision
is made, until one arrives at the decision \cite{Marsland2015Machine}.
For numerical input features, each decision partitions the data
\cite{aggarwal2015data}, for example by comparison to a threshold value.
To construct the tree these cutoff values have to be chosen at every branch. The construction problem turns into an optimization problem when a split criterion is introduced. Common choices are cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
During construction splits minimizing the chosen function are selected.

@@

Once the data was clean and compiled in one directory, the next step was to split the data based on the assembly cycle. For our purpose, we split the dataset into individual data-samples with help of the \textit{action tag}included in the dataset Table~\ref{tab:data_source}. Subsequently, each data-sample was automatically checked for missing sensor values and discarded if so.
% At this point, we have a series of data-samples based on time series. However, we are not interested in a time series analysis, since having the time parameter would not necessarily improve the prediction results, but rather make the approach more complex, and more data would be needed, therefore it was needed to compress each time-series based data-sample into atemporal data-samples.

Each time-series sample was the result of data collected during one machine assembly cycle (MAC). The starting point of one MAC was defined as the very first moment the robotic arm grabs the white disk from the store area and the ending point was defined as the starting of the subsequent MAC, the grabbing of the next white disk in the same area.
To eliminate time as a variable in our dataset, it was needed to transform time-series into feature data suitable describing a MAC in a way that different MACs are easily comparable. For that reason, we defined a set of sampling-conditions that helped us to collect the relevant data during the MAC:
\begin{itemize}
       \item Value of the robot position ($xyz$) while dropping both disks in the conveyor - Gate
       \item Mean conveyor speed value per conveyor band
       \item Absolute deviation ($xy$) value at the quality control check
       \item Absolute quality control value: OK - NOK
\end{itemize}

@@

We compared a total of three different classifier architectures on the data.
A Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using exemplary 
default hyperparameters, which we found to work.
\footnote{To allow exact reproduction of our results source code
 is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

@@

By implementing ML models based on just the initial conditions of the process and capable to predict the quality of the product, would be a great asset for the industrial processes. Within the limits of our work, we predicted with 98\% certainty the product quality by implementing a Decision Tree model with a 6-variables vector as input. 
However, our decision for industrial applications would be the MLP with 88\% accuracy, to guarantee that all passed parts are OK and avoid labeling NOK pieces as OK. For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.

@@

It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area. Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
\vspace{0.1cm}
\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture. 
To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.

@@

\textbf{Dataset size}; as the starting point we collected as many data points as the ones found in the iris Dataset \cite{fisher_1936}. The next step was to collect batches of data of around 30 minutes per use case. This process was repeated until accumulate around 15 hours of data.

@@

Pérez M. and Moritz performed writing - original draft, conceptualization, review, and editing; Investigation; Software and Data Curation.
Schmallenbach performed writing - Review \& editing.
Wagner, Heinbach, Steinberg, Steffes-lai, Garcke performed writing - Review.
Burggräf performed supervision of work.

>>>>

\aucores{* Corresponding author. Tel.: +49-271-740-2630; fax: +49-271-740-12628. {\it E-mail address:} fabian.steinberg@uni-siegen.de}

@@

\subsection{Decision Tree}
Decision Trees are essentially binary trees, which work with the input
features at the roots, decisions are made by moving
up the tree to top leaves. At every branch in the tree, a decision
is made, until one arrives at the decision \cite{Marsland2015Machine}.
For numerical input features, each decision partitions the data
\cite{aggarwal2015data}, for example by comparison to a threshold value.
To construct the tree these cutoff values have to be chosen at every branch. The construction problem turns into an optimization problem when a split criterion is introduced. Common choices are cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
During the construction splits minimizing, the selected functions are chosen.

@@

Once the data was cleaned and compiled in one directory, the next step was to split the data based on the assembly cycle. For our purpose, we split the dataset into individual data-samples with help of the \textit{action flags}included in the dataset Table~\ref{tab:data_source}. Subsequently, each data-sample was automatically checked for missing sensor values and discarded if so.
% At this point, we have a series of data-samples based on time series. However, we are not interested in a time series analysis, since having the time parameter would not necessarily improve the prediction results, but rather make the approach more complex, and more data would be needed, therefore it was needed to compress each time-series based data-sample into atemporal data-samples.

Each time-series sample was the result of data collected during one machine assembly cycle (MAC). The starting point of one MAC was defined as the very first moment the robotic arm grabs the white disk from the store area and the ending point was defined as the starting of the subsequent MAC, the grabbing of the next white disk in the same area.
To eliminate time as a variable in our dataset, it was needed to transform time-series into feature data suitable describing a MAC in a way that different MACs are easily comparable. For that reason, we defined a set of sampling-conditions that helped us to collect the relevant data during the MAC:
\begin{itemize}
       \item Value of the robot position ($xyz$) while dropping both disks in the \textit{conveyor - gate}
       \item Mean conveyor speed value per conveyor band
       \item Absolute deviation ($xy$) value at the quality control check
       \item Absolute quality control value: OK - NOK
\end{itemize}

@@

We compared a total of three different classifier architectures on the data,
a Support Vector Machine (SVM), a Multilayer Perceptron (MLP) and a Decision Tree
structure. In this case, we chose to train all three models using exemplary 
default hyperparameters, which we found to work.
\footnote{To allow exact reproduction of our results source code
 is available at \url{https://github.com/manubrain/Demo-Cell-Classification}}

@@

Implementing ML models based on just the initial conditions of the process and capable to predict the quality of the product, would be a great asset for the industrial processes. Within the limits of our work, we predicted with 98\% certainty the product quality by implementing a Decision Tree model with a 6-variables vector as input. 
However, our decision for industrial applications would be the MLP with 88\% accuracy, to guarantee that all passed parts are OK and avoid labeling NOK pieces as OK. For further work, we expect to increase the accuracy of the prediction model by collecting more data-samples and experimenting with other, more complex, ML models.

@@

It is worth to mention the most important points learned during the project implementation. This might help as building blocks for further research in the area. Difficulties at implementing ML models in production are also described by others authors \cite{paleyes2020challenges}.
\vspace{0.1cm}

\textbf{Incompatibility between technologies}; devices configured on the same network presented troubles to share data due to network restrictions, as well as the limitation to access and modify restricted program-code given by the machine manufacture. 
To overcome the situation stated above, it was necessary to reprogram big sections of the machine control system.

@@

\textbf{Dataset size}; as the starting point we collected as many data points like the ones found in the iris Dataset \cite{fisher_1936}. The next step was to collect batches of data of around 30 minutes per use case. This process was repeated until accumulate around 15 hours of data.

@@

Pérez M. and Wolter performed writing - original draft, conceptualization, review, and editing; investigation; software and data curation.
Schmallenbach performed writing - review \& editing.
Wagner, Heinbach, Steinberg, Garcke, and Steffes-lai performed writing - review.
Burggräf performed supervision of work.
